---
title: "Lifecycle and mental health"
author: "Ishani Makwana, Henry Hirsch and Ei Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```

```{r}
# Import Libraries
rm(list=ls())
library(readr)
library(ggplot2)
library(tidyr)
library(corrplot)
library(ezids)
```

```{r init}
url <- 'https://raw.githubusercontent.com/eitanaka/DATS6101_Final_Project_Team2/main/data_set/geo_socio_health_df.csv'
master_df<- read_csv(url)
```

## Abstract
Need edited

## Introcuction
In project 1, we investigated how health risk behaviors are associated with health outcomes and health status. Now we are trying to examine whether there is any significant influence on mental health due to lifestyle, socio-economic factors, and covid-19 in the United States. Census tracts will be used in calculating and analyzing all the different datasets. This research will help us in identifying and expecting what factors have significantly impacted mental health and well-being in the United States in 2020.  


### Data sets
Need edited (Describe about 4 data set and how we create)

### Variables of interest
CountyFIPS: a character column containing the FIPS code for each county.
GEOID: a character column containing the unique ID for each county.
StateAbbr: a character column containing the abbreviation for the state where each county is located.
CountyName: a character column containing the name of each county.
BINGE: numeric columns representing percentages of adults in each county that reported binge drinking
DEPRESSION: numeric columns representing percentages of adults in each county that reported binge depression
LPA: numeric columns representing percentages of adults in each county that reported less physical activity
MHLTH: numeric columns representing percentages of adults in each county that reported poor mental health
SLEEP: numeric columns representing percentages of adults in each county that reported insufficient sleep.
MT_Total: Total marital status
MT_Never Married: numeric columns representing percentages of adults in each county who were categorized as never married
MT_Now married: numeric columns representing percentages of adults in each county who were categorized as now married.
MT_Divorces: numeric columns representing percentages of adults in each county who were categorized as having got divorces.
MT_Separated: numeric columns representing percentages of adults in each county who were categorized as couple who separated.
MT_Widowed: numeric columns representing percentages of adults in each county who were categorized as having a certain marital status.
EA_Total: Total education population.
EA_Less than high school graduate:numeric columns representing percentages of adults in each county who were categorized as studied less than high school
EA_High school graduate:numeric columns representing percentages of adults in each county who were categorized who are high school graduate.
EA_college or associate's degree: numeric columns representing percentages of adults in each county who were categorized who did college or associate's degree
EA_Bachelor's degree: numeric columns representing percentages of adults in each county who were categorized as completed bachelor's degree
EA_Graduate or professional degree:numeric columns representing percentages of adults in each county who were categorized as having a certain educational graduate or professional degree.
MI_Estimate: numeric column representing the median household income in each county.
Total Population: numeric column representing the total population of each county.
CT_Total: numeric column representing the percentages of the population in each county that take total commute time in percentage
CT_<10: numeric column representing the percentages of the population in each county that take commute time less than 10min
CT_10-14: numeric column representing the percentages of the population in each county that take commute time between 10 -14min
CT_20-24: numeric column representing the percentages of the population in each county that take commute time between 20 -24min
CT_25-29: numeric column representing the percentages of the population in each county that take commute time between 25 -29min
CT_30-34: numeric column representing the percentages of the population in each county that take commute time between 30 -34min
CT_35-44: numeric column representing the percentages of the population in each county that take commute time between 35 -44min
CT_45-54: numeric column representing the percentages of the population in each county that take commute time between 45 -54min
CT_55-59: numeric column representing the percentages of the population in each county that take commute time between 55 -59min
CT_60-64: numeric column representing the percentages of the population in each county that take commute time between 60 -64min
CT_65-74: numeric column representing the percentages of the population in each county that take commute time between 65 -74min
CT_75-84: numeric column representing the percentages of the population in each county that take commute time between 75 -84min
CT_85plus: numeric column representing the percentages of the population in each county that take commute time more than 85 plus minutes

### Initial SMART Question
Need edited
1) Why does the United States have a large number of people with depression and mental health issues? Is the lifestyle, socio-economic factors, and covid-19 in the States leading people towards poor mental health?

2) How can we expect predictors to contribute to increased depression and poor mental health?

## EDA
Need edited

#### Handle Null Values
```{r}
master_df <- na.omit(master_df)
colSums(is.na(master_df[6:length(master_df)]))
```

### Basic EDA
Need edited

#### Handle Outlier
```{r}
```

## Data Structure
Need edited
```{r}
str(master_df)
```


## Summary Statictics
Need edited
```{r}
summary(master_df)
```

### Descriptive Statistics
Need edited

### Correlations
```{r}
cor_matrix <- cor(master_df[,6:length(master_df)])
View(cor_matrix)

# Create 6 subset for cor_matrix or cor_heatmap
dep_mth_df <- subset(master_df, select = "DEPRESSION")
dep_mth_df <- cbind(dep_mth_df, master_df[,9])

# Data frame containing depression, mhlth, health risk behaviors
dep_mth_hrb <- dep_mth_df
dep_mth_hrb["BINGE"] <- master_df[,6]
dep_mth_hrb["LPA"] <- master_df[,8]
dep_mth_hrb["SLEEP"] <- master_df[,10]

# Data frame containing depression, mhlth, MT
dep_mth_mt <- cbind(dep_mth_df, master_df[12:16])
# Data frame containing depression, mhlth, EA, MI, Pop
dep_mth_ea_mi_pop <- cbind(dep_mth_df, master_df[18:24])
# Data Frame containing depression, mhlth, MI, Pop, CT
dep_mth_ct <- cbind(dep_mth_df, master_df[26:34])
# Data Frame containing depression, mhlth, ES 
dep_mth_es <-cbind(dep_mth_df, master_df[36:41])
# Data Frame containing depression, mhlth, others
dep_mth_geo <- cbind(dep_mth_df, master_df[42:length(master_df)])

# A set of cormatrix
cor_matrix_HRB <- cor(dep_mth_hrb)
cor_matrix_MT_EA <- cor(dep_mth_mt)
cor_matrix_EA_MI_POP <- cor(dep_mth_ea_mi_pop)
cor_matrix_CT <- cor(dep_mth_ct)
cor_matrix_ES <- cor(dep_mth_es)
cor_matrix_GEO <- cor(dep_mth_geo)

# Plot
corrplot(cor_matrix_HRB, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
corrplot(cor_matrix_MT_EA, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
corrplot(cor_matrix_EA_MI_POP, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
corrplot(cor_matrix_CT, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
corrplot(cor_matrix_ES, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
corrplot(cor_matrix_GEO, method = "circle", type = "upper", order = "hclust", addCoef.col = "black", tl.col = "black", tl.srt = 45, cl.pos = "n")
```

### Variable Selection
Need edited
```{r}

```

### Hypothesis Testing
Need edited
```{r}
```

### EDA Interpretation?
Need edited

## Model Building
Need edited
```{r}

```

### Check Assumption for Model Buiding?
Need edited

### Building Model
Need edited

### Model Assessment?
Need edited

## Result
Need edited

## Discussion
Need edited

### Limitations
Need edited

### Further Research
Need edited

## Conclusion
Need edited

## References
Need edited
# Reference links to datasets:
https://chronicdata.cdc.gov/500-Cities-Places/PLACES-Local-Data-for-Better-Health-Census-Tract-D/cwsq-ngmh
https://gisgeography.com/us-county-map/
https://www.ers.usda.gov/data-products/county-level-data-sets/county-level-data-sets-download-data/
https://data.census.gov/
https://www.anl.gov/dis/county-economic-impact-index
https://www.census.gov/programs-surveys/community-resilience-estimates/data/datasets.html
https://github.com/NREL/hsds-examples

