---
title: "Lifecycle and mental health"
author: "Ishani Makwana, Henry Hirsch and Ei Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```

```{r init}
url <- 'https://raw.githubusercontent.com/eitanaka/DATS6101_Final_Project_Team2/main/data_set/geo_socio_health_df.csv'
master_df <- read_csv(url)
```

## Abstract
Need edited

## Introcuction
In project 1, we investigated how health risk behaviors are associated with health outcomes and health status. Now we are trying to examine whether there is any significant influence on mental health due to lifestyle, socio-economic factors, and covid-19 in the United States. Census tracts will be used in calculating and analyzing all the different datasets. This research will help us in identifying and expecting what factors have significantly impacted mental health and well-being in the United States in 2020.  


### Data sets
Need edited (Describe about 4 data set and how we create)

### Variables of interest?
Need edited

### Initial SMART Question
Need edited
```{r}

```

## EDA
Need edited

### Basic EDA
Need edited
```{r}

```

### Descriptive Statistics
Need edited

### Hypothesis Testing
Need edited

### EDA Interpretation?
Need edited

## Model Building
Need edited
```{r}

```

### Check Assumption for Model Buiding?
Need edited

### Building Model
Need edited

### Model Assessment?
Need edited

## Result
Need edited

## Discussion
Need edited

### Limitations
Need edited

### Further Research
Need edited

## Conclusion
Need edited

## References
Need edited
