---
title: "Lifecycle and mental health"
author: "Ishani Makwana, Henry Hirsch and Ei Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```

```{r}
# Import Libraries
rm(list=ls())
library(readr)
library(ggplot2)
library(tidyr)
library(corrplot)
library(ezids)
library(car)
library(rpart)
library(rpart.plot)
library(rattle)
library(tree)
```

```{r init}
url <- 'https://raw.githubusercontent.com/eitanaka/DATS6101_Final_Project_Team2/main/data_set/geo_socio_health_df.csv'
master_df<- read_csv(url)
master_df <- master_df[,-1]
```

## Abstract
Need edited

An abstract is an overview of a research project that seeks to explore the relationship between mental health and various socio-economic and lifestyle factors, as well as the impact of COVID-19 in the United States.The aim is to answer the question of whether there is a significant influence on mental health due to these factors in the US, and data will be analyzed at the census tract level using 11 different datasets. The abstract highlights the main objectives, methods, results, and conclusions of the research, while the introduction sets the stage by discussing the relevance of the research question and the data sets used.This question is relevant to the project's aim and can guide the data analysis and interpretation.

## Introduction
In project 1, we investigated how health risk behaviors are associated with health outcomes and health status.We have 11 different datasets that we have made used of. We have tried importing all the datasets from the google drive where all datasets has been uploaded.Now, we are trying to examine whether there is any significant influence on mental health due to lifestyle, socio-economic factors, and covid-19 in the United States. Census tracts will be used in calculating and analyzing all the different datasets. This research which is going to be very interesting to look at identifying what factors have significantly impacted mental health and well-being in the United States in 2020. 

### Data sets
Need edited (Describe about 4 data set and how we create)
We have used of 10 different datasets and the one which we are going to use from the previous Data Science project1. 

### Initial SMART Question
Need edited
1) Why does the United States have a large number of people with depression and mental health issues? Is the lifestyle, socio-economic factors, and covid-19 in the States leading people towards poor mental health?

2) How can we expect predictors to contribute to increased depression and poor mental health?

## EDA
Need edited
Let us work on some data manipulation and visualization tasks by renaming some columns in the dataframe and the second part of your code creates two histograms. The first histogram (dep_hist) shows the distribution of tract-level depression rates, and the second histogram (mhlth_hist) shows the distribution of tract-level poor mental health rates.
```{r}
# To rename some columns in a data frame to make them more readable and easier to work with.This is done by using the "colnames" function to first select the column names that match the original names, and then assigning new names.
colnames(master_df)[colnames(master_df) == "MT_Never Married"] <- "mt.nev.mar"
colnames(master_df)[colnames(master_df) == "MT_Now married"] <- "mt.now.mar"
colnames(master_df)[colnames(master_df) == "Total Population"] <- "tot.pop"
colnames(master_df)[colnames(master_df) == "EA_Less than high school graduate"] <- "ea.less.hs.deg"
colnames(master_df)[colnames(master_df) == "EA_High school graduate"] <- "ea.hs.deg"
colnames(master_df)[colnames(master_df) == "EA_college or associate's degree"] <- "ea.col.ass.deg"
colnames(master_df)[colnames(master_df) == "EA_Bachelor's degree"] <- "ea.ba.deg"
colnames(master_df)[colnames(master_df) == "EA_Graduate or professional degree"] <- "ea.grad.prof.deg"
```

```{r}
# Create a new data only including numerical variable
numeric_vars <- sapply(master_df, is.numeric)
num_df <- master_df[, numeric_vars]
```

#### Basic Information
```{r}
head(num_df)
str(num_df)
```

#### Handle Null Values
```{r}
colSums(is.na(num_df))
num_df <- na.omit(num_df)
colSums(is.na(num_df))
```
The output will be a numeric vector with the number of missing values in each column. If all values are 0, then there are no missing values in the selected columns.

#### Handle Outlier
```{r}
colSums(num_df == 0.0)

new_num_df <- outlierKD2(num_df, num_df[[1]], rm=TRUE)
new_num_df <- new_num_df[,1:(ncol(new_num_df)-2)]

# loop through all columns
for (col_name in colnames(num_df)[2:ncol(num_df)]) {
  # remove outliers
  new_num_df <- outlierKD2(new_num_df, new_num_df[[col_name]], rm=TRUE)
  new_num_df <- na.omit(new_num_df)
  new_num_df <- new_num_df[,1:(ncol(new_num_df)-2)]
}
new_num_df <- new_num_df[,1:(ncol(new_num_df)-1)]
```

### Boxplots for checking outliers
```{r}
# with outliers
par(mfrow=c(8, 8))
par(mar=c(1, 1, 1, 1))
for (i in 1:ncol(num_df)) {
  boxplot(num_df[[i]], main=names(num_df)[i])
}

# without outliers
par(mfrow=c(8, 8))
par(mar=c(1, 1, 1, 1))
for (i in 1:ncol(new_num_df)) {
  boxplot(new_num_df[[i]], main=names(new_num_df)[i])
}
```
### Scatter plot for checking outliers (Depression)
```{r}
# Scatter plots with fit line for Depression and other dependent variables
for (col in names(new_num_df)) {
  if (col != "DEPRESSION") {
    plot_data <- data.frame(x = new_num_df$DEPRESSION, y = new_num_df[[col]])
    plot <- ggplot(plot_data, aes(x = x, y = y)) + 
      geom_point() +
      geom_smooth(method = "lm", se = FALSE) +
      xlab("Depression") +
      ylab(col)
    print(plot)
  }
}
```

### Scatter plot for checking outliers (MHLTH)
```{r}
# Scatter plots with fit line for mhlth and other dependent variables
for (col in names(new_num_df)) {
  if (col != "MHLTH") {
    plot_data <- data.frame(x = new_num_df$MHLTH, y = new_num_df[[col]])
    plot <- ggplot(plot_data, aes(x = x, y = y)) + 
      geom_point() +
      geom_smooth(method = "lm", se = FALSE) +
      xlab("mhlth") +
      ylab(col)
    print(plot)
  }
}
```

### Data Structure
Need edited
It can be useful to get a quick overall structure of the data frame before performing further analyses.
```{r}
str(new_num_df)
```

### Descriptive Statistics
Need edited
It can be useful to get a overview  of summary statistics of the data frame before performing further analyses.
```{r}
summary(new_num_df)
```

### Histogram for dependent variable
To Check normality of dependent variable
```{r}
# Histograms
# Two histograms: one for the distribution of tract-level depression rates and one for the distribution of tract-level poor mental health rates.
hist(new_num_df$DEPRESSION, main = "Distribution of Tract-level Depression Rates")

hist(new_num_df$MHLTH, main = "Distribution of Tract-level Poor Mental Health Rates")

```
Looking at the histograms, it appears that both variables are approximately normally distributed, although the distribution of tract-level depression rates is skewed to the right, with a larger number of observations in the higher bins. The distribution of tract-level poor mental health rates also appears skewed to the right, but with a more gradual decrease in the number of observations in the higher bins compared to the depression rates histogram.This information is important when selecting statistical methods to analyze these variables, as many methods assume normality. Additionally, the histograms provide a visual representation of the distribution of the variables, which can help in identifying potential outliers or unusual patterns.

### QQ-Plot for dependent variable
To check normality of dependent variable
```{r}
# QQ plots for the distribution of tract-level depression rates and tract-level poor mental health rates.

qqnorm(new_num_df$DEPRESSION, main = "Distribution of Tract-level Depression Rates")
qqline(new_num_df$DEPRESSION)

qqnorm(new_num_df$MHLTH, main = "Distribution of Tract-level Poor Mental Health Rates")
qqline(new_num_df$MHLTH)
```
A QQ plot compares the quantiles of a dataset to the quantiles of a theoretical distribution (in this case, the normal distribution). If the points on the QQ plot are close to a straight line, it indicates that the data are normally distributed.
In this case, the QQ plot for the depression rates appears to deviate from a straight line towards the tails, indicating that the distribution is not perfectly normal. The QQ plot for the poor mental health rates appears to deviate from a straight line even more than the depression rates, indicating that the distribution is even less normal.

We will create a new data frame called num_df that only contains the numeric columns of the original master_df, that can be analyzed using various statistical tools.

### Correlations Test
```{r}
# Create a correlation matrix
cor_matrix <- cor(new_num_df)

# Create two lists which have the names of variables highly correlated (more then 0.3 or less than -0.3)
high_dep_cor_list <- names(which(cor_matrix["DEPRESSION",] > 0.35 | cor_matrix["DEPRESSION",] < -0.35))
high_mhlth_cor_list <- names(which(cor_matrix["MHLTH",] > 0.5 | cor_matrix["MHLTH",] < -0.5))

high_dep_cor_list <- high_dep_cor_list[high_dep_cor_list != "MHLTH"]
high_mhlth_cor_list <- high_mhlth_cor_list[high_mhlth_cor_list != "DEPRESSION"]

length(high_dep_cor_list)  
length(high_mhlth_cor_list)
```

### Correlation Heatmap
```{r}
# Create two correlation matrixes from new_num_df in the above lists
high_dep_cor_mat <- cor(new_num_df[high_dep_cor_list])
high_mhlth_cor_mat <- cor(new_num_df[high_mhlth_cor_list])

high_dep_cor_mat
high_mhlth_cor_mat

# Plot above correlation matrix
corrplot(high_dep_cor_mat, type = "lower", outline.color = "white", 
           colors = c("#6D9EC1", "white", "#E46726"), legend.title = "Correlation", 
           ggtheme = theme_gray, title = "Highly Correlated Variables with DEPRESSION")

corrplot(high_mhlth_cor_mat, type = "lower", outline.color = "white", 
           colors = c("#6D9EC1", "white", "#E46726"), legend.title = "Correlation", 
           ggtheme = theme_gray, title = "Highly Correlated Variables with mhlth")

my_col <- colorRampPalette(c("red", "white", "blue"))(30)

corrplot(high_dep_cor_mat, method = "number", type = "lower", order = "hclust", diag = FALSE, tl.col = "black", tl.cex = 0.8, cl.cex = 0.8, addCoef.col = "black", col = my_col, main = "", mar = c(0,0,0,0))

corrplot(high_mhlth_cor_mat, method = "number", type = "lower", order = "hclust", diag = FALSE, tl.col = "black", tl.cex = 0.8, cl.cex = 0.8, addCoef.col = "black", col = my_col, main = "", mar = c(0,0,0,0))

```

#### VIF Test for Multicollinearity
```{r}
calculate_VIF <- function(data, target_col) {
  X <- data[, !colnames(data) %in% target_col]
  vif <- data.frame(
    Feature = colnames(X),
    VIF = apply(X, 2, function(x) vif(lm(x ~ ., data=X)))
  )
  return(vif)
}

depression_VIF <- calculate_VIF(new_num_df[high_dep_cor_list], "DEPRESSION")

mhlth_VIF <- calculate_VIF(new_num_df[high_mhlth_cor_list], "MHLTH")

depression_VIF
mhlth_VIF
```

### Feature Selection
Need edited
```{r}
dep_features_list <- high_dep_cor_list[high_dep_cor_list != "DEPRESSION"]
mhlth_features_list <- high_mhlth_cor_list[high_mhlth_cor_list != "MHLTH"]

dep_features_list
mhlth_features_list
```

## Model Building
Need edited

### Training and Test Sets
```{r}
library(caret)
set.seed(123)
fold <- floor(runif(nrow(new_num_df),1,11)) 
  new_num_df$fold <- fold
  
test.set <- new_num_df[new_num_df$fold == 1,] 
train.set <- new_num_df[new_num_df$fold != 1,] 

```

### Multiple Linear Regression

#### Model 1: With Highly correlated variables (Health Factors + Socioeconomic Factors)
```{r}
# multiple linear regression model for depression
depression_model_1 <- lm(DEPRESSION ~ OBESITY + PHLTH + ea.hs.deg + ea.grad.prof.deg + MI_Estimate + `CT_>60` + hhd.broad, data = train.set)

# multiple linear regression model for poor mental health
mhlth_model_1 <- lm(MHLTH ~ LPA + OBESITY + PHLTH + SLEEP + ea.hs.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + poverty, data = train.set)

summary(depression_model_1)
summary(mhlth_model_1)

plot(depression_model_1)
plot(mhlth_model_1)
```

#### Model 2: With Highly correlated health related variables
```{r}
# multiple linear regression model for depression
depression_model_2 <- lm(DEPRESSION ~ OBESITY + PHLTH, data = train.set)

# multiple linear regression model for poor mental health
mhlth_model_2 <- lm(MHLTH ~ LPA + OBESITY + PHLTH + SLEEP, data = train.set)

summary(depression_model_2)
summary(mhlth_model_2)

plot(depression_model_2)
plot(mhlth_model_2)
```

#### Model 3: With Highly correlated socioeconomic related variables
```{r}
# multiple linear regression model for depression
depression_model_3 <- lm(DEPRESSION ~ ea.hs.deg + ea.grad.prof.deg + MI_Estimate + `CT_>60` + hhd.broad, data = train.set)

# multiple linear regression model for poor mental health
mhlth_model_3 <- lm(MHLTH ~ ea.hs.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + poverty, data = train.set)

summary(depression_model_3)
summary(mhlth_model_3)

plot(depression_model_3)
plot(mhlth_model_3)
```

#### Model Comparison (ANOVA)
```{r}
# Perform two-way ANOVA test
depression_anova_model <- anova(depression_model_1, depression_model_2, depression_model_3)
mhlth_anova_model <- anova(mhlth_model_1, mhlth_model_2, mhlth_model_3)


xkabledply(depression_anova_model)
xkabledply(mhlth_anova_model)

health.socioecon.dep.anova <- anova(depression_model_2, depression_model_3)
health.socioecon.mhlth.anova <- anova(mhlth_model_2, mhlth_model_3)

xkabledply(health.socioecon.dep.anova)
xkabledply(health.socioecon.mhlth.anova)

```

#### Stepwise Selection (Tuning Multiple Linear Regression Model)
```{r}
# Perform stepwise selection using AIC as the selection criterion
depression_stepwise_model <- step(depression_model_1, direction = "both", trace = 0, k = log(nrow(train.set)), criterion = "AIC")

mhlth_stepwise_model <- step(mhlth_model_1, direction = "both", trace = 0, k = log(nrow(train.set)), criterion = "AIC")

# Print the final selected model
summary(depression_stepwise_model)
summary(mhlth_stepwise_model)
```

#### Best Model vs. Stepwise Model
```{r}
dep_anova_model_2 <- anova(depression_model_1, depression_stepwise_model)
mhlth_anova_model_2 <- anova(mhlth_model_1, mhlth_stepwise_model)

xkabledply(dep_anova_model_2)
xkabledply(mhlth_anova_model_2)
```

#### Best Model Performance
```{r}
dep_predictions <- predict(depression_model_1, newdata = test.set)

# calculate the R-squared value
r_squared <- summary(depression_model_1)$r.squared

# calculate the mean squared error (MSE)
mse <- mean((test.set$DEPRESSION - dep_predictions)^2)

# print the results
cat("R-squared:", r_squared, "\n")
cat("MSE:", mse, "\n")

mhlth_predictions <- predict(mhlth_stepwise_model, newdata = test.set)

# calculate the R-squared value
r_squared <- summary(mhlth_stepwise_model)$r.squared

# calculate the mean squared error (MSE)
mse <- mean((test.set$MHLTH - mhlth_predictions)^2)

# print the results
cat("R-squared:", r_squared, "\n")
cat("MSE:", mse, "\n")
```


### Regression Tree Model
- Splitting the data: The dataset is split into training and testing sets to evaluate the model's performance.
- Building the tree: The regression tree is built using a recursive partitioning algorithm, which splits the data into subsets based on the independent variables that best predict the dependent variable.
- Pruning the tree: The tree is pruned to reduce overfitting and improve generalization to new data.
```{r}
#regression tree model for depression
# control_params1 <- rpart.control(minsplit = 20, cp = 0.0005, maxdepth = 10)
# 
# depression.tree <- rpart(DEPRESSION ~ LPA + ea.hs.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + URBANIZED_AREA_POP_CEN_2010 + pct_URBANIZED_AREA_POP_CEN_2010, data = depression_cor_df, method="class", control = control_params1)
# 
# plot(depression.tree, uniform=TRUE, main="Depression Rate Tree")
# text(depression.tree, use.n=TRUE, all=TRUE, cex=.8)
# 
# p <- prp(depression.tree)
# p$nodepar$lab.cex <- 0.8
# p$nodepar$cex <- 0.8
# p$nodepar$lab.col <- "black"
# 
# 
# # regression tree model for poor mental health
# control_params2 <- rpart.control(minsplit = 20, cp = 0.0005, maxdepth = 10)
# 
# mhlth.tree <- rpart(MHLTH ~ LPA + SLEEP + mt.nev.mar + mt.now.mar + MT_Separated + ea.less.hs.deg + ea.hs.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + ES_Civilian_labor_force_employed + ES_Civilian_labor_force_unemployed, data = mhlth_cor_df, method = "class", control = control_params2)
# 
# plot(mhlth.tree, uniform=TRUE, main="Poor Mental Health Rate Tree")
# text(mhlth.tree, use.n=TRUE, all=TRUE, cex=.8)
# 
# p <- prp(mhlth.tree)
# p$nodepar$lab.cex <- 0.8
# p$nodepar$cex <- 0.8
# p$nodepar$lab.col <- "black"
  

# fancy tree plots
# fancy depression tree
```

```{r}

depression.tree <- rpart(DEPRESSION ~  ACCESS2 + BINGE + CHECKUP + DIABETES + LPA + OBESITY + PHLTH + SLEEP + STROKE + mt.nev.mar + mt.now.mar + MT_Divorces + MT_Separated + MT_Widowed + ea.less.hs.deg + ea.hs.deg + ea.col.ass.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + tot.pop + `CT_<10` + `CT_10-14` + `CT_15-19` + `CT_20-24` + `CT_25-29` + `CT_30-34` + `CT_35-44` + `CT_45-59` + `CT_>60` + ES_Total_labor_force + ES_Civilian_labor_force + ES_Civilian_labor_force_employed + ES_Civilian_labor_force_unemployed + ES_Armed_Forces + ES_Not_in_labor_force + land + urban + poverty + no.ins + disab + no.comp + `broad&comp` + no.eng + sing.mom + live.alone + pub.assist + no.phone + no.plumb + married.kid + hhd.no.comp + hhd.only.phone + hhd.no.int + hhd.broad + index_apr20, data = new_num_df, control = rpart.control(maxdepth = ))

fancyRpartPlot(depression.tree, main = "Depression Rate Tree")

summary(depression.tree)

# fancy mental health tree
mhlth.tree <- rpart(MHLTH ~ ACCESS2 + BINGE + CHECKUP + DIABETES + LPA + OBESITY + PHLTH + SLEEP + STROKE + mt.nev.mar + mt.now.mar + MT_Divorces + MT_Separated + MT_Widowed + ea.less.hs.deg + ea.hs.deg + ea.col.ass.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + tot.pop + `CT_<10` + `CT_10-14` + `CT_15-19` + `CT_20-24` + `CT_25-29` + `CT_30-34` + `CT_35-44` + `CT_45-59` + `CT_>60` + ES_Total_labor_force + ES_Civilian_labor_force + ES_Civilian_labor_force_employed + ES_Civilian_labor_force_unemployed + ES_Armed_Forces + ES_Not_in_labor_force + land + urban + poverty + no.ins + disab + no.comp + `broad&comp` + no.eng + sing.mom + live.alone + pub.assist + no.phone + no.plumb + married.kid + hhd.no.comp + hhd.only.phone + hhd.no.int + hhd.broad + index_apr20, data = new_num_df, control = rpart.control(maxdepth = ))


fancyRpartPlot(mhlth.tree, main = "Poor Mental Health Rate Tree")

summary(mhlth.tree)

# pruning trees
# pruned depression tree
# pruned.depression.tree.2 <- prune(depression.tree.2, cp = 0.01)
# fancyRpartPlot(pruned.depression.tree.2)
# 
# # pruned mental health tree
# pruned.mhlth.tree.2 <- prune(mhlth.tree.2, cp = 0.01)
# fancyRpartPlot(pruned.mhlth.tree.2)

```

```{r}
# creating trees using testing and training data
train.dep.tree <- rpart(DEPRESSION ~  ACCESS2 + BINGE + CHECKUP + DIABETES + LPA + OBESITY + PHLTH + SLEEP + STROKE + mt.nev.mar + mt.now.mar + MT_Divorces + MT_Separated + MT_Widowed + ea.less.hs.deg + ea.hs.deg + ea.col.ass.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + tot.pop + `CT_<10` + `CT_10-14` + `CT_15-19` + `CT_20-24` + `CT_25-29` + `CT_30-34` + `CT_35-44` + `CT_45-59` + `CT_>60` + ES_Total_labor_force + ES_Civilian_labor_force + ES_Civilian_labor_force_employed + ES_Civilian_labor_force_unemployed + ES_Armed_Forces + ES_Not_in_labor_force + land + urban + poverty + no.ins + disab + no.comp + `broad&comp` + no.eng + sing.mom + live.alone + pub.assist + no.phone + no.plumb + married.kid + hhd.no.comp + hhd.only.phone + hhd.no.int + hhd.broad + index_apr20, data = train.set, control = rpart.control(maxdepth = ))

fancyRpartPlot(train.dep.tree, main = "Training Depression Rate Tree")
summary(train.dep.tree)

train.mhlth.tree <- rpart(MHLTH ~ ACCESS2 + BINGE + CHECKUP + DIABETES + LPA + OBESITY + PHLTH + SLEEP + STROKE + mt.nev.mar + mt.now.mar + MT_Divorces + MT_Separated + MT_Widowed + ea.less.hs.deg + ea.hs.deg + ea.col.ass.deg + ea.ba.deg + ea.grad.prof.deg + MI_Estimate + tot.pop + `CT_<10` + `CT_10-14` + `CT_15-19` + `CT_20-24` + `CT_25-29` + `CT_30-34` + `CT_35-44` + `CT_45-59` + `CT_>60` + ES_Total_labor_force + ES_Civilian_labor_force + ES_Civilian_labor_force_employed + ES_Civilian_labor_force_unemployed + ES_Armed_Forces + ES_Not_in_labor_force + land + urban + poverty + no.ins + disab + no.comp + `broad&comp` + no.eng + sing.mom + live.alone + pub.assist + no.phone + no.plumb + married.kid + hhd.no.comp + hhd.only.phone + hhd.no.int + hhd.broad + index_apr20, data = train.set, control = rpart.control(maxdepth=4))

fancyRpartPlot(train.mhlth.tree, main = "Poor Mental Health Rate Tree")

summary(train.mhlth.tree)
```

#### Regression Tree Performance
- Evaluating the model: The model is evaluated using various metrics such as mean squared error (MSE), root mean squared error (RMSE), and R-squared.
- Validating the model: The model is validated using the testing set to assess its ability to generalize to new data.
- Tuning the model: The model is tuned by adjusting the hyperparameters to improve its performance.
- Interpreting the model: The regression tree is interpreted to gain insights into the relationships between the independent variables and the dependent variable.
```{r}
# Generate predicted values for test set
test.set$pred.depression <- predict(train.dep.tree, newdata = test.set)

# Calculate evaluation metrics
MSE <- mean((test.set$DEPRESSION - test.set$pred.depression)^2)
R2 <- 1 - sum((test.set$DEPRESSION - test.set$pred.depression)^2) / sum((test.set$DEPRESSION - mean(test.set$DEPRESSION))^2)

# Print evaluation metrics
cat("R-squared:", R2, "\n")
cat("MSE:", MSE, "\n")

# The R-squared value of 0.399 suggests that the regression tree model explains 39.9% of the variation in the data, which is a moderate level of explanation.
# The MSE (Mean Squared Error) of 6.05 represents the average squared difference between the predicted values and the actual values, with a higher value indicating worse performance.

test.set$pred.mhlth <- predict(train.mhlth.tree, newdata = test.set)
# Calculate evaluation metrics
MSE <- mean((test.set$MHLTH - test.set$pred.mhlth)^2)
R2 <- 1 - sum((test.set$MHLTH - test.set$pred.mhlth)^2) / sum((test.set$MHLTH - mean(test.set$MHLTH))^2)

# Print evaluation metrics
cat("R-squared:", R2, "\n")
cat("MSE:", MSE, "\n")

# The regression tree model with MHLTH as the target variable has an R-squared value of 0.685, indicating that 68.5% of the variability in the MHLTH variable can be explained by the model. 
# The mean squared error (MSE) is 1.07, which means that on average, the model's predictions are off by 1.07 units from the actual values. .
# The root mean squared error (RMSE) is 1.04, which is the same as the standard deviation of the residuals.
# This indicates that the model's predictions have a standard deviation of 1.04 around the actual values. Overall, these metrics suggest that the model has a moderate level of predictive power for the MHLTH variable.
```

## Result
Need edited

## Discussion
Need edited

### Limitations
Need edited

### Further Research
Need edited

## Conclusion
Need edited

## References
Need edited
# Reference links to datasets:
https://chronicdata.cdc.gov/500-Cities-Places/PLACES-Local-Data-for-Better-Health-Census-Tract-D/cwsq-ngmh
https://gisgeography.com/us-county-map/
https://www.ers.usda.gov/data-products/county-level-data-sets/county-level-data-sets-download-data/
https://data.census.gov/
https://www.anl.gov/dis/county-economic-impact-index
https://www.census.gov/programs-surveys/community-resilience-estimates/data/datasets.html
https://github.com/NREL/hsds-examples
