---
title: "Lifecycle and mental health"
author: "Ishani Makwana, Henry Hirsch and Ei Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```

```{r}
# Import Libraries
rm(list=ls())
library(readr)
library(ggplot2)
library(tidyr)
```

```{r init}
url <- 'https://raw.githubusercontent.com/eitanaka/DATS6101_Final_Project_Team2/main/data_set/geo_socio_health_df.csv'
master_df <- read_csv(url)
```

## Abstract
Need edited

## Introcuction
Need edited

### Data sets
Need edited (Describe about 4 data set and how we create)

### Initial SMART Question
Need edited

### Variable of Interest
Need edited

## EDA
Need edited

#### Handle Null Vales
```{r}
master_df <- na.omit(master_df)
colSums(master_df)
```

### Basic EDA
Need edited

#### Handle Null Values
```{r}
master_df <- na.omit(master_df)

colSums(is.na(master_df))

```

#### Handle Outlier
```{r}

```

### Descriptive Statistics
Need edited

### Hypothesis Testing
Need edited

### Correlations
```{r}
cor_matrix <- cor(master_df[,6:50])
View(cor_matrix)
```

### EDA Interpretation?
Need edited

## Model Building
Need edited
```{r}

```

### Check Assumption for Model Buiding?
Need edited

### Building Model
Need edited

### Model Assessment?
Need edited

## Result
Need edited

## Discussion
Need edited

### Limitations
Need edited

### Further Research
Need edited

## Conclusion
Need edited

## References
Need edited
